Mainstreaming Scientific Racism

### 2022-11-02 talk/talk.qmd
full draft of talk

# Introduction

@@

# Mainstreaming race science

@@

---

*[focal topics by journal over time]*

# Conclusion

- Race & intelligence research did not appear to originate in *MQ* and spread to other journals
- Instead, *Intelligence* and *PID* were the primary venues used to legitimize this psychological form of race science
- "The race science is coming from inside the house!"

>>>>

# Introduction {visibility="uncounted"}

@@

# Mainstreaming race science {visibility="uncounted"}

@@

## Focal topics, by journal, over time

![](img/08_presentation.png)

# Conclusions {visibility="hidden"}
## Conclusions

- Most Pioneer-funded researchers did not publish heavily in *MQ*
- Race & intelligence research did not appear to originate in *MQ*

- Instead, *Psychological Reports* and later *Intelligence* and *PID* were the primary venues for this psychological form of race science
- "The race science is coming from inside the house!"
